Mapping malaria by sharing spatial information between incidence and prevalence datasets

### 2020-06-15 si.tex
Add plots of the priors.

@@

% Current address notes

\section{Crossvalidation schemes}

@@

@@

\clearpage
\subsection{Full model predictions}
\subsubsection{Madagascar}

@@

\subsubsection{Senegal}

@@

\clearpage
\subsubsection{Indonesia}

@@

\subsection{Full model fields}

\subsubsection{Senegal}

@@

\clearpage
\subsubsection{Madagascar}

@@

>>>>

\tableofcontents

@@

% Current address notes
\clearpage
\section{Crossvalidation schemes}

@@

\clearpage
\section{Out-of-sample scatter plot}

@@

\clearpage
\section{Full model predictions}
\subsection{Madagascar}

@@

\subsection{Senegal}

@@

\clearpage
\subsection{Indonesia}

@@

\section{Full model fields}

\subsection{Senegal}

@@

\clearpage
\subsection{Madagascar}

@@

\clearpage
\section{Priors}

\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_density.png}

\caption{Probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
\label{dens}
\end{figure}

\includegraphics[width =  0.8\textwidth]{figures/spatial_pc_logdensity.png}

\caption{Log probability density of the penalised complexity prior for the range and marginal standard deviation for the spatial random field as used in Madagascar models..}
\label{logdens}
\end{figure}
